### 2015-01-21 paper/Diversity_MS.tex
Fixed reference bugs

\usepackage[nomarkers]{endfloat} %Figures and tables at the end of the document
\usepackage{pdflscape}	% for landscape pages
\usepackage{mathtools}	% For equations etc.
\usepackage[osf]{mathpazo} % palatino font package
\usepackage{fixltx2e}	% includes subscripts
\usepackage{ms}     	% load the manuscript style template - may need to change this for PeerJ

@@

	The methods we used involved several steps of data collection, geometric morphometrics analyses and comparisons of morphological diversity. For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.

%Methods flow chart
	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth,height=0.8\textheight]{figures/methods_flowchart_paper.png}

@@

	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files %\citep[uncompressed files preserve greater detail,][]{RHOI2013}. Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull pictures along with the mandibles \citep{Finlay2013m}. Copyright restrictions from the other museums prevent public sharing of their images however they are available on request.

@@

%********************************
\bibliographystyle{sysbio} 
\bibliography{refs_thesis} %This is a copy of my refs_thesis file so it has more references than are included in the paper

>>>>

\usepackage[nomarkers]{endfloat} %Figures and tables at the end of the document
\usepackage{pdflscape}	% for landscape pages
\usepackage{mathtools}	% For equations etc.
\usepackage[osf]{mathpazo} % palatino font package
\usepackage{fixltx2e}	% includes subscripts
\usepackage{ms}     	% load the manuscript style template - may need to change this for PeerJ
\usepackage{hyperref}

@@

	The methods we used involved several steps of data collection, geometric morphometrics analyses and comparisons of morphological diversity. For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.  	
%Methods flow chart
	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth,height=0.8\textheight]{figures/methods_flowchart_paper.png}

@@

	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep{RHOI2013}. 
	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull pictures along with the mandibles \citep{Finlay2013m}. Copyright restrictions from the other museums prevent public sharing of their images however they are available on request.

@@

%********************************
\bibliographystyle{sysbio} 
\bibliography{refs_paper}
